\chapter{Evaluation}

In this chapter we provide a final evaluation regarding the results achieved during the course of this work. Initially, we estimate an approximate test coverage achieved on Dynamics 365 for Finance and Operation with the analyzed business processes. Then, we elaborate on the total amount of resources needed (in terms of time) in order to acquire the required knowledge necessary to work and develop on the application and to apply said knowledge to create the required test cases. Finally, we give an insight regarding the usefulness of the project as a whole with a final focus on the applicability that it could have in a context with tighter schedules.

%********************************** %First Section  **************************************
\section{Coverage} 

Providing an accurate approximation on the total coverage of our test suite is a particularly complex task given the large and ever-expanding nature of the application that we worked on. In order to discuss this task as precisely as possible we will evaluate this topic in relation to three different metrics: total coverage of the chosen business processes (under normal conditions), amount of covered edge cases and degree of coverage of the application as a whole. 
The five business processes that we have chosen as a starting point for our work were covered completely in relation to the initially defined requirements. Knowing this fact, it is important to specify that in order to respect the project time constraint we intentionally left out (during the requirements definition) some additional activities that could have been involved in the covered processes. Such activities were mainly related to: Advanced warehouse management (warehouse configuration, partial shipment, inventory counting and replenishment), advanced production activities (material exceptions, BOM configuration/customization) and testing related to the interaction between the application and the handheld WMS software. In regard to the considered edge cases we focused mainly on user inputs that could have caused possible issues with the application. This meant focusing the expansion of test cases on invalid (wrong type), out of range or unacceptable input values in forms and unexpected interaction with UI elements (e.g. a missing step in a business process). Limitations in terms of time and experience brought us to the decision of excluding more complex kinds of edge cases and advanced techniques such as verifying performance under heavy load and role/duties/privileges -based testing.
If we look at the application as a whole (considering all the available functionalities that it offers), we will notice that our test cases only covered a small portion of all the provided features. Despite this fact we have to consider that not every business process will have the same relevance to the final customer and that identifying the core functionalities to prioritize during the testing activities was particularly important considered the limited time at our disposal. Furthermore, the future availability of the provided documentation will surely decrease the time required to apply the described techniques to previously untested portion of the application.

%********************************** %Second Section  **************************************
\section{Resources} 

When we analyze the (temporal) resources required to complete this project it is important to take into consideration some concepts that influenced the final outcome of the work. In this regard we want to differentiate two aspects that played a role on this subject: time needed to acquire the required knowledge and write the documentation and time to develop the test cases.
The first activity relates to the resources necessary for a new team member to acquire the knowledge necessary in order to apply the testing techniques on the Dynamics 365 for Finance and Operation application and to create the documentation of the development process. Insight regarding the acquisition of this knowledge is particularly useful for the reader to have a more precise outlook regarding the scope of the work and for a company to decide if it wants to start implementing this kind of techniques on their applications. Regarding this first concept it is important to notice that a big portion of the project time was spent familiarizing with the application, completing the necessary training activities and creating the documentation needed to share the final know-how (indicatively around 60\% of the total time). This set of tasks was naturally of central importance for us in order to develop effectively and, in the end, to provide some useful knowledge to the company. However it is easy to understand how a team member already part of the company would not need all the training activities that were previously described. Furthermore, the process of creating the documentation that describes the steps for the creation of a test case and the particulars of the used framework has to be performed only once and can later be uses indefinitely by the other members.
The second aspect that we want to describe is related to the time required for a developer (already in possession of the previously mentioned know-how) to implement the described testing activities for a new business process (which very important for the company in order to have a general idea of the expected amount of work needed when a new testing activity is started). We have estimated that a testing activity (from the creation of the first recording to the end of the expansion process) can be concluded in a matter of hours if there is a good underlying knowledge of the underlying business process and on what has to be tested and expanded. Giving a more precise estimation if fairly difficult given the fact that the size (and variability) of the tested feature(s) strongly influences the total time required to complete the testing activities. Naturally, our development process (around 40\% of the total work) was much longer because of the learning curve involved (it was a first time approach, no previous know-how was provided) and the number of different business processes considered. 

%********************************** %Third Section  **************************************
\section{Usefulness and Applicability} 

The project has certainly provided useful information to the company regarding the testing activities that could potentially be implemented in their future and currently ongoing projects. The fact that we have provided a well documented overlook on the whole process is naturally a positive aspect particularly helpful in relation to the scarce availability of official documentation regarding certain technical aspects of the application. 
In regard to the general level of applicability of this work we should take into consideration the fact that we worked on a project developed internally by the company and not strictly influenced by deadlines imposed on us by a specific client (as mentioned before, Trade+ is developed as a starting point for customers that can request their own personalization to be built on top of it). Applying testing techniques in projects that have tighter schedules that need to be followed in order to deliver specific functionalities in time would certainly be a more difficult task and would require a careful planning activity to be performed by the company. Despite this fact, we believe that introducing some form of testing in most projects can greatly improve the reliability of the developed software and, because of this reason, it may represents a worthwhile investment (from both the company and the costumer) in order to produce an higher quality product.